The influence of resource use on yield versus quality trade-off in Australian vineyards

### 2023-08-19 article.tex
fixed numbers with new models

\begin{table}[]
\caption{Summary of models; their predictors, covariates and variable interactions.}\label{tab:tab1}
  \resizebox{\textwidth}{!}{\begin{tabular}{@{}ccccc@{}}
    \toprule
    & \textbf{Response} & \textbf{Predictors} & \textbf{Covariates} & \textbf{Interactions} \\ \midrule
    \textbf{Model 1} & Yield & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 2} & ${ \textrm{Yield}}\over{ \textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested \end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * scope one Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular} \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 3} & {$\textrm{Yield} {\times} \textrm{Average Sale Price}$} & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A\\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 4} & Average Sale Price & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\
        \\ \end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * Scope One Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular}
        \\
        \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
     \textbf{Model 5} &  Average Sale Price & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}} Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}} Year * Region\end{tabular}
        \end{tabular}}
\end{table}

@@

Each model had a high $R^2$ value, indicating that a most of the variance within the data was described by the models (see Table~\ref{tab:modelsummary}). The models were were found to be a good fit, with overall F-tests being statistically significant (P $<$ 2.200E-16). And, aside from 3 variables, F-tests across each model's variables were also significant (with all being at least, P $<$ 0.05). The three exceptions were: scope one emissions in Model 3 (P=0.22) and Model 4 (P=0.0.39), and the interaction between area harvested and water used in model 2 (P=0.22). Note that, scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values and because it was strongly correlated to the response variable in every model (except model 5); especially for Models 1 and 4 (Table \ref{tab:pearson_correlation}). A full list of regression coefficients 95\% CIs and p-values for each of the four models is provided in the appendix. % You gotta add these to the appendix in a more readable fashion
\par
\begin{table}[]
  \caption{Summary of models; their performance, F-statistics and Residual error.}\label{tab:modelsummary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
          \toprule
           & $\mathbf{R^2}$ & \textbf{\begin{tabular}[c]{@{}c@{}} Adjusted\\ $\mathbf{R^2}$ \end{tabular}} & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 1\\ \end{tabular}} & 9.072E-01 & 9.061E-01 & 7.753E+02 & 2.200e-16 & 3.065E-01 & 4.913E+02 & 1.000E-01 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 2\\ \end{tabular}} & 7.951E-01 & 7.770E-01 & 4.403E+01 & 2.200e-16 & 4.722E-01 & 1.085E+03 & 2.200E-01 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 3\\ \end{tabular}} & 9.753E-01 & 9.748E-01 & 1.885E+03 & 2.200e-16 & 1.589E-01 & 7.111E+01 & 3.000E-02 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 4\\ \end{tabular}} & 9.669E-01 & 9.638E-01 & 3.095E+02 & 2.200e-16 & 1.904E-01 & 9.528E+01 & 4.000E-02 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 5\\ \end{tabular}} & 0.9089 & 0.9004 & 107.2 & 2.200e-16 & 0.3155 & 262.04 & 0.10 \\ \bottomrule
          \end{tabular}
        }
\end{table}

>>>>

\begin{table}[]
\caption{Summary of models; their predictors, covariates and variable interactions.}\label{tab:tab1}
  \resizebox{\textwidth}{!}{\begin{tabular}{@{}ccccc@{}}
    \toprule
    & \textbf{Response} & \textbf{Predictors} & \textbf{Covariates} & \textbf{Interactions} \\ \midrule
    \textbf{Model 1} & Yield & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 2} & ${ \textrm{Yield}}\over{ \textrm{Area Harvested}}$ & \begin{tabular}[c]{@{}c@{}}Water Used\\ scope one Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * scope one Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular} \\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 3} & {$\textrm{Yield} {\times} \textrm{Average Sale Price}$} & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & N/A\\
    \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
    \textbf{Model 4} & Average Sale Price & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested\\ Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}}Area Harvested * Scope One Emissions\\ Area Harvested * Water Use\\ Year * Region\end{tabular}
        \\
        \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
     \textbf{Model 5} &  Average Sale Price & \begin{tabular}[c]{@{}c@{}}Water Used\\ Scope One Emissions\end{tabular} & \begin{tabular}[c]{@{}c@{}} Year\\ GI Region\end{tabular} & \begin{tabular}[c]{@{}c@{}} Year * Region\end{tabular}
        \end{tabular}}
\end{table}

@@

Each model had a high $R^2$ value, indicating that a most of the variance within the data was described by the models (see Table~\ref{tab:modelsummary}). The models were were found to be a good fit, with overall F-tests being statistically significant (P $<$ 2.200E-16). And, aside from 3 variables, F-tests across each model's variables were also significant (with all being at least, P $<$ 0.05). The three exceptions were: scope one emissions in Model 3 (P=0.22) and Model 4 (P=0.0.39), and the interaction between area harvested and water used in model 2 (P=0.22). Note that, scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values and because it was strongly correlated to the response variable in every model (except model 5); especially for Models 1 and 4 (Table \ref{tab:pearson_correlation}). A full list of regression coefficients 95\% CIs and p-values for each of the four models is provided in the appendix. % You gotta add these to the appendix in a more readable fashion
\par
\begin{table}[]
  \caption{Summary of models; their performance, F-statistics and Residual error.}\label{tab:modelsummary}
      \resizebox{\textwidth}{!}{
        \begin{tabular}{@{}cccccccc@{}}
          \toprule
           & $\mathbf{R^2}$ & \textbf{\begin{tabular}[c]{@{}c@{}} Adjusted\\ $\mathbf{R^2}$ \end{tabular}} & \textbf{F-Statistic} & \textbf{P-Value} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual\\ Standard Error\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Sum\\ of Squares\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ of Squares\end{tabular}} \\ \midrule
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 1\\ \end{tabular}} & 0.9072 & 0.9061 & 775.3 & 2.200e-16 & 0.3065 & 491.3 & 0.1 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 2\\ \end{tabular}} & 0.8291 & 0.8141 & 55.07 & 2.200e-16 & 0.4312
           & 905.03 & 0.19 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 3\\ \end{tabular}} &0.9753 &0.9748 & 1885 & 2.200e-16 & 0.1589 & 71.11 & 0.03 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 4\\ \end{tabular}} & 0.9091 & 0.9006 & 106.1 & 2.200e-16 & 0.3153  & 261.41 & 0.10 \\
          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\
          \textbf{\begin{tabular}[c]{@{}c@{}}Model 5\\ \end{tabular}} & 0.9089 & 0.9004 & 107.2 & 2.200e-16 & 0.3155 & 262.04 & 0.10 \\ \bottomrule
          \end{tabular}
        }
\end{table}
